### 2017-11-07 Draft2/AsymptoticNotation.tex
Cleanup all the limits
Add prefix

I will mainly use the $\sim$ relation to analyze complexity. It is defined as follows:
\begin{align*}
f \sim g \Biconditional \lim_{n \to \infty} \frac f g = 1
\end{align*}
This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

I will also introduce the cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
\begin{align*}
f \FluteLess g \Biconditional \lim_{n \to \infty} \frac f g < 1
\end{align*}
\subsection{Properties}
\label{subsec:AsymptoticProperties}

@@

The following theorem states that $\sim$ can "merge", or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.

@@

\begin{theorem}
\label{thm:RemovesLowerOrderTerms}
	If $\lim_{n \to \infty} \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
\end{theorem}

>>>>

I will mainly use the $\sim$ relation to analyze complexity. It is defined as follows:
\begin{align*}
f \sim g \Biconditional \ExprNToInfty \frac f g = 1
\end{align*}
This is read as ``$f$ is asymptotic to $g$'' or ``$f$ and $g$ are asymptotic.'' {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

I will also introduce the cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
\begin{align*}
f \FluteLess g \Biconditional \ExprNToInfty \frac f g < 1
\end{align*}
\subsection{Properties}
\label{subsec:AsymptoticProperties}

@@

The following theorem states that $\sim$ can ``merge,'' or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.

@@

\begin{theorem}
\label{thm:RemovesLowerOrderTerms}
	If $\ExprNToInfty \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
\end{theorem}
